A GRASP algorithm for the concrete delivery problem.

### 2023-08-24 Article/article.tex
save

\begin{table}[hbt]
    \centering
    \caption{Parameters of the real-world instances}
    \label{tab:problem_parameters}
    \small
    %    \resizebox*{\textwidth}{!}{
    \begin{tabularx}{\textwidth}{Xr}
        \toprule
        \multicolumn{1}{c}{Parameter}  &
        \multicolumn{1}{c}{Value} \\ \midrule
 Time window ($\tau^w$)  & 60 min    \\
 Unloading duration ($\tau_c^u$)  & 2 min$/m^3$   \\
 Cleaning duration ($\rho$)    & 10 min  \\
        Adjustment duration ($\alpha$)                                                & 10 min                    \\
        Max travel time ($\Delta$)                                                    & 120 min                   \\
        Min working time ($M_T$)                                                      & 180 min                   \\
        Max working time ($N_T$)                                                      & 480 min                   \\
        Max overtime duration ($O_T$)                                                 & 120 min                   \\
        Max delay between two consecutive deliveries of the same order $\gamma^1$)   & 20 min                    \\
        Max delay between two consecutive deliveries of different orders ($\gamma^2)$ & 25 min                    \\
        Penalty of unfulfilled orders ($\beta_1$)                                     & 10,0000                   \\
        Penalty of first delivery delay ($\beta_2$)                                   & 1,0000                    \\
        Penalty for driver underutilization  ($\beta_3$)                              & 30                        \\
        Driver overtime penalty $ (\beta_4$)                                          & 20                        \\
        \bottomrule
    \end{tabularx}
    %    }
\end{table}
%  the travel cost ($TC$), the penalties associated with unfulfilled orders ($PUO$), the sum of the first delivery delays ($FDD$) for each customer, the sum of the driver underutilization costs ($DUC$) and driver overtime costs ($DOC$).
The table \ref*{tab:all_instances} contains the detailed results for all instances with a stop criterion of 3600 seconds. The table shows the demand of each instance, the average and the best values of the objective function when solving each instance five times. All daily orders of the small instances are completely served by our algorithm within these five replications, as shown in column $UQ$, which reports the undelivered quantity. $99.57\%$ and $99.5\%$ of the total demands are served for the medium and large sets. The sum of the driver underutilization costs ($DUC$) is high for medium and large instances. This indicates the underutilization of the scheduled fleet. Some drivers are not scheduled at all or work very little. The sum of driver overtime costs ($DOC$) is also high for these instances. This can be explained by the fact that the algorithm prefers to put certain drivers on overtime rather than use a driver who has to travel to another plant for a delivery, which would increase the travel costs ($TC$).

$FDD$ is the sum of the delays of the first deliveries.  For the small instances, all but one of the first deliveries are on time. For the other instances sets, there is at least one customer with a late first delivery.
To get an idea of the actual delay per customer, we report $mFDD$, which is the maximum delay of all first deliveries. This tells us that we have a maximum delay that varies between 0 and $35.7$ minutes for small instances, $16.8$ and $60$ minutes for medium instances, and $56$ to 60 minutes for large instances.

\begin{table}[!ht]
    \centering
    \caption{Results with all instances}
    \label{tab:all_instances}
    \resizebox{\textwidth}{!}{
    \begin{tabular}{llcccccccccccccc}
    \toprule
    &                 &          & \multicolumn{6}{c}{Avg} & \multicolumn{6}{c}{Best}  \\
    \cmidrule(l){4-9} \cmidrule(l){10-16}
     &  & Demand & $TC$ & $UQ$ & $FDD$ & $DUC$ & $DOC$ & \multirow[c]{2}{*}{Z} & $TC$ & $UQ$ & $FDD$ & $mFDD$ & $DUC$ & $DOC$ & \multirow[c]{2}{*}{Z} \\
     &  & ($m^3$) & (min) & ($m^3$) & (min) & (min) & (min) &  & (min) & ($m^3$) & (min) & (min) & (min) & (min) &  \\
    \midrule
    \multirow[c]{8}{*}{Small} & C_13_11_12_1 & 226.5 & 1,243.5 & 0.0 & 0.0 & 10.8 & 0.0 & 1,568.3 & 1,243.5 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 1,243.5 \\
     & C_13_5_8_1 & 267.0 & 745.1 & 0.0 & 0.0 & 0.0 & 0.0 & 745.1 & 745.1 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 745.1 \\
     & C_18_6_11_2 & 333.5 & 753.3 & 0.0 & 0.0 & 145.9 & 0.0 & 5,130.0 & 753.3 & 0.0 & 0.0 & 0.0 & 118.7 & 0.0 & 4,315.1 \\
     & C_15_4_7_2 & 375.0 & 1,015.6 & 0.0 & 0.0 & 148.2 & 150.5 & 8,470.9 & 1,015.4 & 0.0 & 0.0 & 0.0 & 123.4 & 110.3 & 6,924.5 \\
     & C_19_7_8_2 & 388.0 & 1,747.2 & 0.0 & 0.0 & 349.8 & 159.0 & 15,421.6 & 1,781.8 & 0.0 & 0.0 & 0.0 & 186.0 & 0.0 & 7,361.5 \\
     & C_29_10_14_3 & 613.5 & 3,510.1 & 0.0 & 59.5 & 194.6 & 331.9 & 75,488.1 & 3,493.4 & 0.0 & 59.5 & 35.7 & 120.5 & 60.0 & 67,810.4 \\
     & C_31_8_11_3 & 776.0 & 2,314.8 & 0.0 & 0.0 & 804.3 & 640.7 & 39,256.8 & 2,278.2 & 0.0 & 0.0 & 0.0 & 503.5 & 617.0 & 29,722.9 \\
     & C_35_9_10_3 & 937.5 & 4,175.5 & 0.0 & 0.0 & 222.1 & 669.3 & 24,224.7 & 4,163.1 & 0.0 & 0.0 & 0.0 & 243.3 & 570.0 & 22,863.2 \\
     \cmidrule(l){1-16}

@@

We can observe that the loading operations for each plant are non-overlapping and the unloading operations occur sequentially, one after the other, at the worksite. Plant $0$ is in charge of both orders of customer $8$. In figure~\ref*{fig:plant0}, order $o_8$ is served before $o_9$ starting at the due time. Each row on the figure represents the pairs of loading and unloading tasks performed by a driver. The number near a task references the order.  Figure~\ref*{fig:plant2} shows how the loading bay is alternately assigned to orders $o_{13}$ and $o_7$ between $10:00$ and $14:00$ a.m. Driver $26$ starts its service at plant $0$, serves order $o_9$ four times and travels to plant $2$ to perform the last delivery of order $o_{13}$. Driver $25$ also loads at both plants $0$ and $1$.

We report for this solution of instance $C29\_10\_14\_3$ a $FDD$ of $59.5$ minutes. The gantt chart indicates that customers $4,5$ whom need their deliveries at $07:00$ a.m. have all a first late delivery. The reason for these delays is that the drivers assigned to plant $1$ starts their earliest shift at $06:05$, and $06:20$. And it takes $59$($63$) minutes travel time to visit customer $4$($5$) from this plant. So it appears that the big value of $FDD$ we find in our results may be caused by a bad schedule of the drivers shifts.

@@

The medium instance $C\_104\_42\_47\_8$ has an unserved customer with a demand of 12 $m^3$ and a due time of $07:00$. Upon investigation, we find that even if we have $104$ drivers in this instance, the number of drivers starting their shift before the due time is not sufficient to serve this customer within the time window of 60 minutes that we define. So the value of $UQ$ we report in Table~\ref*{tab:all_instances} seems to be the optimal given the driver shift schedule given to our algorithm. We confirmed this observation by lifting the driver shift and overtime constraints and resolving our instances five more times. All orders are now completely served, and at each run. Table~\ref*{tab:lift_shift_constraints} compare the average values of the results of the tables \ref*{tab:all_instances} and \ref*{tab:all_instances_no_shift}. We found that for small instances, the maximum delay dropped to zero, and for medium (large) instances, it was reduced by almost 60\% (40\%) on average. This suggests that when we input a good work schedule, our algorithm works effectively to ensure that all orders are filled and that delays for first deliveries and travel costs are minimized. We can see that the average travel time decreases for all instances, except for the large one where the difference is not notable.

\begin{table}[!h]
    \centering
    \small
    \caption{Comparaison of the average results with and without shift and overtime constraints}
    \label{tab:lift_shift_constraints}
    \resizebox{0.8\textwidth}{!}{
    \begin{tabular}{lcccccccc}
    \toprule
     & \multicolumn{4}{c}{Default parameters}&\multicolumn{4}{c}{$M_T=0$, $N_T,O_T=\infty$, $H_k=0$} \\
     \cmidrule(l){2-5} \cmidrule(l){6-9}
     & $TC$ & $PUO$ & $FDD$ & $mFDD$ & $TC$ & $PUO$ & $FDD$ & $mFDD$ \\
     & (min) & ($m^3$) & (min) & (min) & (min) & ($m^3$) & (min) & (min) \\
    \midrule
    Small & 1,938.13 & 0.00 & 7.44 & 4.47 & 1,842.97 & 0.00 & 0.00 & 0.00 \\
    Medium & 15,007.28 & 10.26 & 400.45 & 46.31 & 14,879.19 & 0.00 & 74.11 & 17.87 \\
    Large & 22,045.81 & 13.26 & 935.49 & 56.93 & 22,454.09 & 0.00 & 187.51 & 34.76 \\
    \bottomrule
    \end{tabular}
    }
\end{table}

@@

    \caption{Results with all instances without shift constraints}

@@

\subsubsection{Comparisons with the industry partner historical operations}

\begin{table}[htb]
    \centering
    \caption{Comparaison with historical operations}
    \label{tab:comp_unibeton}
    \begin{tabular}{lccccccc}
    \toprule
     & & & \multicolumn{5}{c}{Distance} \\
     \cmidrule(l){3-3} \cmidrule(l){4-8}
     & Demand & Distance &  $\gamma^1=5$&  $\gamma^1=10$ & $\gamma^1=15$ & $\gamma^1=20$& $\gamma^1=25$ \\
     & ($m^3$) & ($Km$)  &($Km$)  & ($Km$) & ($Km$) &($Km$)  &($Km$)  \\
    \midrule
    C_13_5_8_1 & 267.0 & 543.1 & 523.5 & 523.5 & 523.5 & 523.5 & 523.5 \\
    C_76_40_43_6 & 1,160.5 & 5,244.7 & 5,101.2 & 4,706.1 & 4,673.3 & 4,645.6 & 4,732.4 \\
    C_116_67_78_8 & 1,839.5 & 11,664.8 & 11,895.8 & 11,035.3 & 11,064.2 & 10,928.9 & 10,823.4 \\
    C_15_4_7_2 & 375.0 & 789.3 & 702.3 & 702.9 & 702.3 & 703.5 & 702.3 \\
    C_18_6_11_2 & 333.5 & 555.1 & 491.7 & 471.5 & 471.5 & 471.5 & 471.5 \\
    C_94_63_70_7 & 1,746.5 & 12,011.2 & 12,957.1 & 11,965.5 & 11,915.6 & 11,657.1 & 11,475.7 \\
    \bottomrule
    \end{tabular}
    \end{table}

@@

In this section, we analyse the impact on the solution when we change some parameters of our problem, and how some components of the objective function are influencing each other.

 % That's because the goals of minimizing travel cost and not delaying the first delivery are sometimes in conflict: to ensure that the first delivery is not late, drivers assigned to one plant often have to travel to another. And since all plants are used in large cases, this can increase travel times.

%  Therefore, we can use our algorithm for fleet sizing or as a submodule of a driver scheduling algorithm.

@@

We conducted some tests with different values $\gamma^1$ varying between 5 and 25 minutes, without any shifts or overtime constraints on the drivers. The influence of the value of the maximum time delay between two consecutive deliveries of the same order is demonstrated in Figure~\ref*{fig:gamma1_influence}. For small instances, all customers are served on time regardless of the value of $\gamma^1$. For medium (large) instances, all customers are served with $\gamma^1$ starting at 15 (20) minutes. The delay of the initial delivery decreases as $\gamma^1$ increases. These results confirm the fact that with a high $\gamma^1$ value, plants have more flexibility to delay ongoing deliveries to make room for new ones or make customers wait until drivers are available. By increasing the maximum time delay from 10 to 20 minutes, the first delivery delay is reduced by over 50\% for the medium and large size instances. The average travel time does not significantly change regardless of the value of $\gamma^1$.

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.8\textwidth]{gamma1.pdf}
    \small
    \caption{Influence of the maximum time delay ($\gamma^1$) between consecutive deliveries of the same order. }
    \label{fig:gamma1_influence}
\end{figure}

@@

We ran 5 tests on our data and obtained two solutions: one with the shortest travel time and another with the smallest first delivery delay. Figures 1 and 2 illustrate the comparisons between travel times and first delivery delays for these solutions. It's clear that as the first delivery delay decreases, the travel time increases, and vice versa. This highlights a trade-off between minimizing travel time and minimizing first delivery delay and leads the decision maker to find a balance between reducing operating costs and compromising customer satisfaction.

\begin{figure}[!ht]
    \centering
    \resizebox{1.25\textwidth}{!}{
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\linewidth]{travel.pdf}
        \vspace*{-2em}
        \caption{travel cost}
        \label{fig:travel}
    \end{subfigure}%
    \hfill% Horizontal space between the subfigures
    \begin{subfigure}{0.5\textwidth}
        \includegraphics[width=\linewidth]{FDD.pdf}
        \vspace*{-2em}
        \caption{first delivevery delay}
        \label{fig:fdd}
    \end{subfigure}
    \vspace*{-1mm}
    }
\end{figure}

@@

Il serait intéressant de voir l'effet des paramètres gamma 1 et gamma 2 différents par clients et /ou ordre. Également le temps de service différent par client.

l'algorithme serait intéressant à utiliser dans le cadre d'un

%  Therefore, we can use our algorithm for fleet sizing or as a submodule of a driver scheduling algorithm.

\vspace{0.1in}

>>>>

\begin{table}[hbt]
    \centering
    \caption{Parameters of the real-world instances}
    \label{tab:problem_parameters}
    \small
    \begin{tabularx}{\textwidth}{Xr}
        \toprule
        \multicolumn{1}{c}{Parameter}  &
        \multicolumn{1}{c}{Value} \\ \midrule
 Time window ($\tau^w$)  & 60 min    \\
 Unloading duration ($\tau_c^u$)  & 2 min$/m^3$   \\
 Cleaning duration ($\rho$)    & 10 min  \\
        Adjustment duration ($\alpha$)                                                & 10 min                    \\
        Max travel time ($\Delta$)                                                    & 120 min                   \\
        Min working time ($M_T$)                                                      & 180 min                   \\
        Max working time ($N_T$)                                                      & 480 min                   \\
        Max overtime duration ($O_T$)                                                 & 120 min                   \\
        Max delay between two consecutive deliveries of the same order $\gamma^1$)   & 20 min                    \\
        Max delay between two consecutive deliveries of different orders ($\gamma^2)$ & 25 min                    \\
        Penalty of unfulfilled orders ($\beta_1$)                                     & 10,0000                   \\
        Penalty of first delivery delay ($\beta_2$)                                   & 1,0000                    \\
        Penalty for driver underutilization  ($\beta_3$)                              & 30                        \\
        Driver overtime penalty $ (\beta_4$)                                          & 20                        \\
        \bottomrule
    \end{tabularx}
\end{table}

The table \ref*{tab:all_instances} contains the detailed results for all instances with a stop criterion of 3600 seconds. The table shows the demand of each instance, the average, and the best values of the objective function when solving each instance five times. All daily orders of the small instances are completely served by our algorithm within these five iterations, as shown in column $UQ$, which reports the undelivered quantity. For the medium and large instances, $99.57\%$ and $99.5\%$ of the total demands are delivered. The sum of driver underutilization costs ($DUC$) is high for medium and large instances. This indicates the underutilization of the scheduled fleet. Some drivers are not scheduled at all or work very little. The sum of driver overtime costs ($DOC$) is also high for these instances. This can be explained by the fact that the algorithm prefers to put drivers on overtime rather than use a driver who has to travel to another plant for a delivery, which would increase travel costs ($TC$).

FDD represents the sum of the delays of the first deliveries. In the case of small instances, all but one of the first deliveries are on time. However, for the other instance sets, there is at least one customer with a late first delivery. To provide insight into the actual delay experienced by customers, we report mFDD, which is the maximum delay among all first deliveries. This information reveals that for small instances, the maximum delay ranges between 0 and 35.7 minutes. For medium instances, it varies from 16.8 to 60 minutes, and for large instances, it falls within the range of 56 to 60 minutes.

\begin{table}[htb]
    \centering
    \caption{Results with all instances}
    \label{tab:all_instances}
    \resizebox{\textwidth}{!}{
    \begin{tabular}{llcccccccccccccc}
    \toprule
    &                 &          & \multicolumn{6}{c}{Avg} & \multicolumn{6}{c}{Best}  \\
    \cmidrule(l){4-9} \cmidrule(l){10-16}
     &  & Demand & $TC$ & $UQ$ & $FDD$ & $DUC$ & $DOC$ & \multirow[c]{2}{*}{Z} & $TC$ & $UQ$ & $FDD$ & $mFDD$ & $DUC$ & $DOC$ & \multirow[c]{2}{*}{Z} \\
     &  & ($m^3$) & (min) & ($m^3$) & (min) & (min) & (min) &  & (min) & ($m^3$) & (min) & (min) & (min) & (min) &  \\
    \midrule
    \multirow[c]{8}{*}{Small} & C_13_11_12_1 & 226.5 & 1,243.5 & 0.0 & 0.0 & 10.8 & 0.0 & 1,568.3 & 1,243.5 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 1,243.5 \\
     & C_13_5_8_1 & 267.0 & 745.1 & 0.0 & 0.0 & 0.0 & 0.0 & 745.1 & 745.1 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 745.1 \\
     & C_18_6_11_2 & 333.5 & 753.3 & 0.0 & 0.0 & 145.9 & 0.0 & 5,130.0 & 753.3 & 0.0 & 0.0 & 0.0 & 118.7 & 0.0 & 4,315.1 \\
     & C_15_4_7_2 & 375.0 & 1,015.6 & 0.0 & 0.0 & 148.2 & 150.5 & 8,470.9 & 1,015.4 & 0.0 & 0.0 & 0.0 & 123.4 & 110.3 & 6,924.5 \\
     & C_19_7_8_2 & 388.0 & 1,747.2 & 0.0 & 0.0 & 349.8 & 159.0 & 15,421.6 & 1,781.8 & 0.0 & 0.0 & 0.0 & 186.0 & 0.0 & 7,361.5 \\
     & C_29_10_14_3 & 613.5 & 3,510.1 & 0.0 & 59.5 & 194.6 & 331.9 & 75,488.1 & 3,493.4 & 0.0 & 59.5 & 35.7 & 120.5 & 60.0 & 67,810.4 \\
     & C_31_8_11_3 & 776.0 & 2,314.8 & 0.0 & 0.0 & 804.3 & 640.7 & 39,256.8 & 2,278.2 & 0.0 & 0.0 & 0.0 & 503.5 & 617.0 & 29,722.9 \\
     & C_35_9_10_3 & 937.5 & 4,175.5 & 0.0 & 0.0 & 222.1 & 669.3 & 24,224.7 & 4,163.1 & 0.0 & 0.0 & 0.0 & 243.3 & 570.0 & 22,863.2 \\
     \cmidrule(l){1-16}

@@

We can see that the loading operations for each plant do not overlap, and the unloading operations occur sequentially, one after the other, at each worksite. Plant $0$ is responsible for both orders from customer $8$. In the figure~\ref*{fig:plant0}, order $o_8$ is served before $o_9$, starting at the due time. Each row in the figure represents the pairs of loading and unloading tasks performed by a driver. The number next to a task refers to the order.  Figure~\ref*{fig:plant2} shows how the loading bay is alternately assigned to orders $o_{13}$ and $o_7$ between $10:00$ and $14:00$. Driver $26$ starts his service at plant $0$, serves order $o_9$ four times, and travels to plant $2$ to make the final delivery of order $o_{13}$. Driver $25$ also loads at both plants $0$ and $1$.

We report a $FDD$ of $59.5$ minutes for this solution of instance $C29\_10\_14\_3$. The Gantt chart shows that the customers $4$ and $5$ who need their deliveries at $07:00$ all have a late first delivery. These delays are due to the work schedules of the drivers assigned to Plant 1. These drivers start their shifts at the earliest at $06:05$ and $06:20$, and it takes them $59$ to $63$ minutes to reach the customers. This finding suggests that the relatively high FDD values in our results may be related to suboptimal scheduling of drivers' hours in our instances.

@@

The medium instance $C\_104\_42\_47\_8$ has an unserved customer with a demand of 12 $m^3$ and a due time of $07:00$. Upon investigation, we find that even if we have $104$ drivers in this case, the number of drivers who start their shift before t$07:00$ is not enough to serve this customer within the 60-minute window we defined. Thus, the value of $UQ$ that we report in the table~\ref*{tab:all_instances} appears to be optimal given the driver shift schedule given as input to our algorithm. We confirmed this observation by removing the driver start shift and overtime constraints and resolving our instances five more times. All orders are now fully serviced on each run. The table~\ref*{tab:lift_shift_constraints} compares the averages of the results from  the tables \ref*{tab:all_instances} and \ref*{tab:all_instances_no_shift}. We found that for small instances the maximum delay dropped to zero, and for medium (large) instances it was reduced by almost 60\% (40\%) on average. This suggests that when we input a good work schedule, our algorithm works effectively to ensure that all orders are filled and that delays for first deliveries and travel costs are minimized. We can see that the average travel time decreases in all cases except the large one, where the difference is not significant.

\begin{table}[!h]
    \centering
    \small
    \caption{Comparison of the average results with and without shift and overtime constraints}
    \label{tab:lift_shift_constraints}
    \resizebox{0.8\textwidth}{!}{
    \begin{tabular}{lcccccccc}
    \toprule
     & \multicolumn{4}{c}{Default parameters}&\multicolumn{4}{c}{$M_T=0$, $N_T,O_T=\infty$, $H_k=0$} \\
     \cmidrule(l){2-5} \cmidrule(l){6-9}
     & $TC$ & $UQ$ & $FDD$ & $mFDD$ & $TC$ & $UQ$ & $FDD$ & $mFDD$ \\
     & (min) & ($m^3$) & (min) & (min) & (min) & ($m^3$) & (min) & (min) \\
    \midrule
    Small & 1,938.13 & 0.00 & 7.44 & 4.47 & 1,842.97 & 0.00 & 0.00 & 0.00 \\
    Medium & 15,007.28 & 10.26 & 400.45 & 46.31 & 14,879.19 & 0.00 & 74.11 & 17.87 \\
    Large & 22,045.81 & 13.26 & 935.49 & 56.93 & 22,454.09 & 0.00 & 187.51 & 34.76 \\
    \bottomrule
    \end{tabular}
    }
\end{table}

@@

    \small
    \caption{Results with all instances without shift and overtime constraints}

@@

@@

In this section, we analyze the effect on the solution when we change some parameters of our problem and how some components of the objective function influence each other.

@@

We ran additional tests with different values of $\gamma^1$, varying between 5 and 25 minutes, with no shifts or overtime constraints on the drivers. The influence of the value of the maximum time delay between two consecutive deliveries of the same order is shown in figure~\ref*{fig:gamma1_influence}. For small instances, all customers are served on time regardless of the value of $\gamma^1$. For medium (large) instances, all customers are served with $\gamma^1$ starting at 15 (20) minutes. The delay of initial delivery decreases as $\gamma^1$ increases. These results confirm the fact that when $\gamma^1$ is high, plants have more flexibility to delay current deliveries to make room for new ones or to make customers wait until drivers are available. Increasing the maximum delay from 10 to 20 minutes reduces the first delivery delay by over 50\% for the medium and large cases. The average delivery time does not change significantly regardless of the value of $\gamma^1$.

\begin{figure}[!h]
    \centering
    \includegraphics[width=1\textwidth]{gamma1.pdf}
    \small
    \caption{Influence of the maximum time delay ($\gamma^1$) between consecutive deliveries of the same order. }
    \label{fig:gamma1_influence}
\end{figure}

@@

We ran five tests on our dataset and obtained two solutions per instance: one that prioritizes the shortest travel time and another that seeks the smallest first delivery delay. Figure~\ref*{fig:trade_off} visually represents the trade-off between travel time and first delivery delay for these solutions. It is clear that as the first delivery delay decreases, the travel time increases, and conversely when the travel time is minimized, the first delivery delay tends to be longer. This result is expected because drivers assigned to a plant often need to travel to another plant to ensure that the first delivery remains on schedule. This trade-off highlights the challenge decision-makers face in finding the right balance between minimizing operational costs and meeting customer satisfaction.

\begin{figure}[!h]
    \centering
    \includegraphics[width=1\textwidth]{Trav_FDD.pdf}
    \small
    \caption{Trade-off between minimizing travel cost VS minimizing first delivery delay }
    \label{fig:trade_off}
\end{figure}

@@

In this paper, we investigated a variant of the concrete delivery problem, where customers can order different types of concrete from different production centers, which must be delivered at the same time. To solve this problem, we introduced a mathematical model and a heuristic solution based on Greedy Randomized Adaptive Search. Our analysis, using a dataset derived from our partner's historical data, demonstrated the effectiveness of our algorithm in making good decisions within a reasonable time. Furthermore, our model incorporates constraints related to working hours, making our heuristic a valuable tool for designing weekly schedules for company drivers. Our GRASP algorithm performed exceptionally well on \cite{kinable2014concrete} datasets, indicating its reliability. For future work, it would be interesting to address datasets with different unloading times at construction sites or to explore different scenarios regarding the number of simultaneous deliveries and the maximum time between two consecutive deliveries at a construction site. We can also study the problem using a stochastic or robust methodology to account for the uncertainty of the parameters in a real-world setting. As a contribution to the literature on CDP, we provide a mathematical formulation for our variant, contribute a dataset, and demonstrate the application of GRASP to solve both our problem and the one studied by \cite{kinable2014concrete}.
\vspace{0.1in}
